Hippocampal replay of experience at real-world speeds

### 2020-10-07 Article.tex

%TC:break Abstract
%the command above serves to have a word count for the abstract
\begin{abstract}
Representations of past and possible future experiences play a critical role in memory and decision-making processes. The hippocampus expresses these types of representations during sharp-wave ripple (SWR) events, and previous work identified a minority of SWRs that contain “replay” of spatial trajectories at ~20x real-world speeds. Efforts to understand replay typically make multiple assumptions about which events to examine and what sorts of representations constitute replay. We therefore lack a clear understanding of both the prevalence and the range of representational dynamics associated with replay. Here we develop a state space model that uses a combination of movement dynamics of different speeds to capture the spatial content and time evolution of replay during SWRs. We find that the large majority of replay events contain spatially coherent, interpretable content. Furthermore, most events progress at real-world, rather than accelerated, movement speeds, consistent with actual experiences.

\end {abstract}
%TC:break main
%the command above serves to have a word count for the abstract

@@

Finally, we specify how likely each movement dynamic is to persist in time versus changing to another dynamic (Figure \ref{1}D) via a state transition matrix between dynamics. In order to be conservative, we assume that each movement dynamic is likely to dominate for \texttildelow100 ms, which is approximately the duration of a SWR event. There is, however, a small probability of switching to one of the other movement dynamics. Accordingly, we set the probability of staying in a dynamic to 0.98 for each 2 ms time step, which corresponds to an expected duration of 100 ms for staying in a particular dynamic (because the Markov assumption of the model means that the probability of staying in a dynamic follows a geometric distribution). Importantly, the data drives the estimated dynamic, so even if the probability of a particular movement dynamic is high, data providing clear evidence for a change in dynamic can, within the time frame of \texttildelow10 ms, drive a change to a different estimated dynamic. In line with this, note that below we show that our results are relatively insensitive to the value of this parameter.

@@

Finally, as mentioned above, we wanted to test the robustness of the model to the choice of probability of staying in a dynamic, because our choice of 0.98 or an expected duration of 100 ms is only based on the expected duration of a SWR. To investigate this we decoded the spiking sequence in Figure \ref{1}A with different probabilities of staying in the same dynamic versus switching to another dynamic (Figure \ref{fig:Figure1-Figure supplement 1}). We found that for a large range of plausible probabilities of staying in one of the dynamics (between 0.96 and 0.993 which corresponds to an expected duration between 25 and 150 ms), the model still correctly identified the sequence dynamics with high probability (Figure \ref{fig:Figure1-Figure supplement 1}A). Furthermore, the probability of latent position remains relatively consistent for these probabilities as well ((Figure \ref{fig:Figure1-Figure supplement 1}B).

@@

We next sought to validate the model on real hippocampal data. We fit the place fields of 31 cells recorded in hippocampus while the rat was performing a spatial alternation task on a W-shaped track, and then applied the decoding algorithm to a SWR with sequential population activity (Figure \ref{2}A, top panel). As expected, we observed that the probability of being in the continuous dynamic is high throughout this event, but the probability of being in a stationary dynamic was also noticeable at the beginning and end of the SWR (Figure \ref{2}A, middle panel). Using our speed classification scheme, this means that the speed of the replay starts slower---as a mixture of continuous and stationary dynamics---and then speeds up and slows down again. This is also evident in the posterior probability of linear position over time. This shows that the replay most likely travels down the center arm and up the right arm (Figure \ref{2}A, bottom panel). We can also see this when we project the maximum of the posterior of this trajectory (the most probable "mental" position) to 2D (Figure \ref{2}C) to better see the spatial trajectory on the maze. Importantly, when we apply the same model using the 2D position of the animal, we get a similar result as when we use the 1D linearized position (Figure \ref{fig:Figure2-Figure supplement 1}A).

@@

As expected, and providing further support for the validity of the method, we observed many replays that were classified as continuous throughout the entirety of the SWR as with the standard decoder(Figure \ref{fig:Figure2-Figure supplement 2}A-F). However, we also observed many events with spatially coherent content that did not have this structure. For example, we observed trajectories that started in one direction and reversed back to the original position (Figure \ref{3}A, Figure \ref{fig:Figure3-Figure supplement 1}B), trajectories that remained fixed in one position (Figure \ref{3}B, Figure \ref{fig:Figure3-Figure supplement 1}G), trajectories that jumped between arms and between dynamics (Figure \ref{3}C-F, Figure \ref{fig:Figure3-Figure supplement 1}F, H, I), and trajectories that were spatially incoherent throughout the SWR (Figure \ref{fig:Figure3-Figure supplement 1}A, D).

@@

Previous work focusing on spatially sequential replay reported that only a minority of events contain sequential spatial content \cite{KarlssonAwakereplayremote2009, FosterReversereplaybehavioural2006, DavidsonHippocampalReplayExtended2009}. We therefore asked what fraction of classified events contain spatially coherent content, which we define as SWRs containing any times with stationary, stationary-continuous mixture, or continuous dynamics (see Methods). We found that 96\% (22478 of 23382) of classified SWRs and 85\% of all SWRs included spatially coherent structure and the prevalence of spatially coherent structure was consistent across animals (Figure \ref{3}F). We then asked what fraction of events contained spatially incoherent content, defined as a SWR containing any times with fragmented or fragmented-continuous mixture dynamics. We found that only 3353 of 23382 or 14\% of classified SWRs had time points with spatially incoherent structure.

@@

Our model is specified in the context of a latent position associated with different movement dynamics. This specification allows us to not only to classify events in terms of their dynamics, but also to quantify the model's certainty in each position estimate at each moment in time given the model parameters. To do so we can compute the cumulative spatial extent of the 95\% highest posterior density (HPD) region of the posterior linear position. Larger values of the cumulative HPD extent indicate the model is less certain about position, because the most probable decoded positions are distributed over more of the track at a given time point. In contrast, lower values indicate that the model is more certain about the estimate of position because the extent of the HPD is more concentrated and covers less of the track. Thus, the HPD provides a complementary measure of spatial coherence, and evaluating it allows us to verify that the events we defined as spatially coherent correspond to events where there is most often high certainty around the position estimates.

Although this is certainly influenced by the dynamics imposed on the model via the movement state transition matrix, because the model is primarily driven by the data, it does not necessarily have to be the case that the two coincide. To show this, as before, we resampled position with replacement for two recording sessions, shuffling the relationship between spiking and spatial information and then fitting the encoding model. The shuffled decodes had much larger spatial coverage than the real data (XX cm vs XX cm, p=2.2e-16, one-sided Mann-Whitney-U, \ref{fig:Figure4-Figure supplement 1}).

We found that spatially coherent events did indeed have lower cumulative HPD sizes than events with fragmented dynamics. Figure \ref{4}A and B show two example SWRs that were classified as having stationary and continuous dynamics, respectively. The bulk of the HPD values at each time step in these SWRs is concentrated in a small portion of the track and the cumulative HPD size is low throughout the SWRs. In contrast, Figure \ref{4}C shows a SWR where the dynamics are fragmented and correspondingly, the HPD is much more spatially diffuse and the cumulative HPD size is much higher. The HPD also provides insights into the moment-by-moment structure of each event, which can change over the time course of a SWR. An example of this change is shown in Figure \ref{4}D, where the cumulative HPD size is small for most of the SWR until the end, at which point the uncertainty of position becomes much higher, reflecting a transition from a spatially coherent to a spatially incoherent representation. Overall, when we examined the average cumulative HPD size for each SWR, grouped by dynamic, we found a clear bimodal split between spatially coherent dynamics and spatially incoherent dynamics (Figure \ref{4}E,). For the spatially coherent dynamics, the cumulative HPD was much lower than the spatially incoherent dynamics (median 24 cm, spatially coherent vs. median 238 cm, spatially incoherent, p=2.2e-16, one-sided Mann-Whitney-U). We note here that while the size of the HPD will be influenced by the dynamic estimated from the data, it remains the case that a continuous or stationary dynamic can correspond to a large HPD region (see outliers in Fig. 4E), indicating less certainty for those specific events.

\begin{figure*}%[tb2]
\centering
\includegraphics[width=0.80\linewidth]{figures/Figure4/Figure4_v6}
\caption{Validation of classification using the 95\% Highest Posterior Density. \textbf{(A-D)}  Examples of the 95 \% Highest Posterior Density. In each column: top panel: Probability of dynamic over time. Shading and labels indicate dynamic categories. Middle panel: Posterior distribution of estimated linear position over time. Red triangle indicates animal's position. Bottom panel: Posterior distribution plot, where black designated the position bins that are included in the 95\% highest posterior density (HPD) region. 4th panel: Cumulative HPD size. \textbf{(E)} Average Cumulative 95\% HPD size for each dynamic category. Spatially coherent events (stationary, stationary-continuous, and continuous) each had much smaller median HPDs than spatially incoherent events (fragmented-continuous, fragmented, and unclassified), p < XX, ranksum tests.}
\label{4}
\end{figure*}

@@

Surprisingly, our results indicate that most events with coherent spatial content are not dominated by the continuous movement dynamic, and thus correspond to trajectories that are stationary or that move relatively slowly compared to their purely continuous counterparts. We therefore examined these events in more detail. We first note that most of the SWRs (16454 of 23382 classified SWRs or 70\%) are well described by a single dynamic (Figure \ref{5}A). Surprisingly, the most common category is stationary-continuous mixtures (9860 of 23382 classified SWRs or 42\%, Figure \ref{5}A). These events contain representations that move at slower speeds (Figure \ref{5}D), and are slightly shorter, on average, than events with continuous dynamics (median duration: stationary-continuous-mixture 72 ms vs. continuous 95 ms, Figure \ref{5}B). Nonetheless, both these slow-moving events and continuous events represented locations that were some distance away from the animal (mean trajectory distance from animal's position: stationary-continuous-mixture 51 cm vs. continuous 42 cm, Figure \ref{5}C). This indicates that the trajectories of these SWRs, like ones that have faster continuous dynamics, do not represent the animal's actual position and cannot be explained by erroneously detected SWRs.

@@

Previous work reported that less than half of SWRs or high-population-activity events contained replay \cite{KarlssonAwakereplayremote2009, FosterReversereplaybehavioural2006, DavidsonHippocampalReplayExtended2009}. This could lead one to the assumption that most events are not spatially coherent or meaningful. Our results indicate that this is not the case: in our dataset, the large majority of SWRs (85\%) contained spatially coherent content, as defined by some combination of stationary or continuous dynamics. These events included decoded representations that were highly spatially concentrated. This was in stark contrast to unclassified events or events that included fragmented dynamics, which were associated with highly distributed decoded spatial representations.

@@

\subsection*{Simulated Data}
Encoding data for Figure \ref{1} and Figure \ref{fig:Figure1-Figure supplement 1} were generated by simulating 15 traversals of a 180 cm linear track. The spiking of 19 neurons was simulated using an inhomogeneous Poisson process where the instantaneous firing rate of each neuron changes according to a Gaussian place field. The Gaussian place fields had a variance of 36 cm and were spaced at 10 cm intervals over the 180 cm track. The decoding data for Figure \ref{1}G was generated by simulating 20,000 linear traversals of the 180 cm track, each with a unique constant speed, starting at 0.5 cm/s and increasing by 0.5 cm/s up to 10,000 cm/s. Each simulated neuron "spiked" when the traversal passed through the peak location of its place field.

@@

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=1.0\linewidth]{figures/Figure1-supplemental1/Figure1_v3_supplemental1}
\caption{The model is robust to change of the probability of persisting in the same dynamic for a wide range of plausible expected durations (25 ms to 150 ms). \textbf{(A)} Each plot shows the probability of each dynamic on simulated data example from Figure 1 with a different diagonal value---which governs the probability of remaining in that dynamic. The corresponding expected duration of staying in the dynamic is listed as duration. The off-diagonal values---the probability of switching to one of the other dynamics---are set to be equally likely with the remainder of the probability, as in Figure \ref{1}D. The diagonal increases from left to right, top to bottom, until the case where the diagonal is one and the off-diagonal is zero---i.e. the case where there is no probability of switching to another dynamic. Shaded regions correspond to the classification as in Figure \ref{1}. \textbf{(B)} The probability of position over time for each diagonal value. Conventions the same as in (A).}
\label{fig:Figure1-Figure supplement 1}
\end{figure*}

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=0.80\linewidth]{figures/Figure2-supplemental1/Figure2_v3-supplemental1}
\caption{Decoding the same SWR in Figure \ref{2} with 2D position using sorted spikes and clusterless decoding, respectively. \textbf{(A)} The left plot shows the spikes from cells arranged by the linear position of the peak of place field as in Figure 2. The middle plot shows the probability of each dynamic over time from the 2D decode. Shaded regions indicate classification category as in Figure 1G and 2. The rightmost plot shows the most probable estimate of the latent position (MAP estimate) with color indicating time. The latent position posterior summed over time is shown in the purple shading. The light grey lines represent the position of the animal over the entire epoch and the magenta dot represents the animal's position. \textbf{(B)} Same as in (A), but with clusterless decoding.}
\label{fig:Figure2-Figure supplement 1}
\end{figure*}

>>>>

%TC:break Abstract
%the command above serves to have a word count for the abstract
\begin{abstract}
Representations of past and possible future experiences play a critical role in memory and decision-making processes. The hippocampus expresses these types of representations during sharp-wave ripple (SWR) events, and previous work identified a minority of SWRs that contain “replay” of spatial trajectories at ~20x real-world speeds. Efforts to understand replay typically make multiple assumptions about which events to examine and what sorts of representations constitute replay. We therefore lack a clear understanding of both the prevalence and the range of representational dynamics associated with replay. Here we develop a state space model that uses a combination of movement dynamics of different speeds to capture the spatial content and time evolution of replay during SWRs. We find that the large majority of replay events contain spatially coherent, interpretable content. Furthermore, most events progress at real-world, rather than accelerated, movement speeds, consistent with actual experiences. 
\end {abstract}
%TC:break main
%the command above serves to have a word count for the abstract

@@

Finally, we specify how likely each movement dynamic is to persist in time versus changing to another dynamic (Figure \ref{1}D) via a state transition matrix between dynamics. In order to be conservative, we assume that each movement dynamic is likely to dominate for \texttildelow100 ms, which is approximately the duration of a SWR event. There is, however, a small probability of switching to one of the other movement dynamics. Accordingly, we set the probability of staying in a dynamic to 0.98 for each 2 ms time step, which corresponds to an expected duration of 100 ms for staying in a particular dynamic (the Markov assumption of the model means that the probability of staying in a dynamic follows a geometric distribution). Importantly, the data drives the estimated dynamic, so even if the probability of a particular movement dynamic is high, data providing clear evidence for a change in dynamic can, within the time frame of \texttildelow10 ms, drive a change to a different estimated dynamic, as in our simulated example. In line with this, note that below we show that our results are relatively insensitive to the value of this parameter.

@@

Finally, as mentioned above, we wanted to test the robustness of the model to the choice of probability of staying in a dynamic, because our choice of 0.98 or an expected duration of 100 ms is only based on the expected duration of a SWR. To investigate this we decoded the spiking sequence in Figure \ref{1}A with different probabilities of staying in the same dynamic versus switching to another dynamic (Figure \ref{fig:Figure1-Figure supplement 1}). We found that for a large range of plausible probabilities of staying in one of the dynamics (between 0.96 and 0.993 which corresponds to an expected duration between 25 and 150 ms), the model still correctly identified the sequence dynamics with high probability (Figure \ref{fig:Figure1-Figure supplement 1}A), demonstrating that data is the most important element in the model. Furthermore, the probability of latent position remains relatively consistent for these probabilities as well (Figure \ref{fig:Figure1-Figure supplement 1}B).

@@

We next sought to validate the model on real hippocampal data. We fit the place fields of 31 cells recorded in hippocampus while the rat was performing a spatial alternation task on a W-shaped track, and then applied the decoding algorithm to a SWR with sequential population activity (Figure \ref{2}A, top panel). As expected, we observed that the probability of being in the continuous dynamic is high throughout this event, but the probability of being in a stationary dynamic was also noticeable at the beginning and end of the SWR (Figure \ref{2}A, middle panel). Using our speed classification scheme, this means that the speed of the replay starts slower---as a mixture of continuous and stationary dynamics---and then speeds up and slows down again. This is also evident in the posterior probability of linear position over time. This shows that the replay most likely travels down the center arm and up the right arm (Figure \ref{2}A, bottom panel). We can also see this when we project the maximum of the posterior of this trajectory (the most probable "mental" position) to 2D to better see the spatial trajectory on the maze (Figure \ref{2}C). Importantly, when we apply the same model using the 2D position of the animal, we get a similar result as when we use the 1D linearized position (Figure \ref{fig:Figure2-Figure supplement 1}A).

@@

As expected, and providing further support for the validity of the method, we observed many replays that were classified as continuous throughout the entirety of the SWR as with the standard decoder (Figure \ref{fig:Figure2-Figure supplement 2}A-F). However, we also observed many events with spatially coherent content that did not have this structure. For example, we observed trajectories that started in one direction and reversed back to the original position (Figure \ref{3}A, Figure \ref{fig:Figure3-Figure supplement 1}B), trajectories that remained fixed in one position (Figure \ref{3}B, Figure \ref{fig:Figure3-Figure supplement 1}G), trajectories that jumped between arms and between dynamics (Figure \ref{3}C, D, F, Figure \ref{fig:Figure3-Figure supplement 1}F, H, I). We also observed SWRs that were spatially incoherent throughout the SWR (Figure \ref{fig:Figure3-Figure supplement 1}A, D).

@@

Previous work focusing on spatially sequential replay reported that only a minority of events contain sequential spatial content \cite{KarlssonAwakereplayremote2009, FosterReversereplaybehavioural2006, DavidsonHippocampalReplayExtended2009}. We therefore asked what fraction of classified events contain spatially coherent content, which we define as SWRs containing any times with stationary, stationary-continuous mixture, or continuous dynamics (see Methods). We found that 96\% (22478 of 23382) of classified SWRs and 85\% of all SWRs included spatially coherent structure and the prevalence of spatially coherent structure was consistent across animals (Figure \ref{3}G). We then asked what fraction of events contained spatially incoherent content, defined as a SWR containing any times with fragmented or fragmented-continuous mixture dynamics. We found that only 3353 of 23382 or 14\% of classified SWRs had time points with spatially incoherent structure (Figure \ref{3}G).

@@

Because our model is specified in the context of a latent position associated with different movement dynamics, it allows us to not only to classify events in terms of their dynamics, but also to quantify the model's certainty in each position estimate at each moment in time given the model parameters. To do so we can compute the cumulative spatial size of the 95\% highest posterior density (HPD) region of the posterior linear position. Larger values of the HPD size indicate the model is less certain about position, because the most probable decoded positions are distributed over more of the track at a given time point. In contrast, lower values indicate that the model is more certain about the estimate of position because the extent of the HPD is more concentrated and covers less of the track. Thus, the HPD provides a complementary measure of spatial coherence, and evaluating it allows us to verify that the events we defined as spatially coherent correspond to events where there is most often high certainty around the position estimates.

We found that spatially coherent events did indeed have lower cumulative HPD sizes than events with fragmented dynamics. Figure \ref{4}A and D show two example SWRs that were classified as having stationary and continuous dynamics, respectively. The majority of the positions in the HPD at each time step in these SWRs is concentrated in a small portion of the track and the cumulative HPD size is low throughout the SWRs. In contrast, Figure \ref{4}C shows a SWR where the dynamics are fragmented and correspondingly, the HPD is much more spatially diffuse and the cumulative HPD size is much higher. The HPD also provides insights into the moment-by-moment structure of each event, which can change over the time course of a SWR. An example of this change is shown in Figure \ref{4}B, where the cumulative HPD size is small for most of the SWR until the end, at which point the uncertainty of position becomes much higher, reflecting a transition from a spatially coherent to a spatially incoherent representation. Overall, when we examined the average cumulative HPD size for each SWR, grouped by dynamic, we found a clear bimodal split between spatially coherent dynamics and spatially incoherent dynamics (Figure \ref{4}E). For the spatially coherent dynamics, the cumulative HPD size was much lower than the spatially incoherent dynamics (median 24 cm, spatially coherent vs. median 238 cm, spatially incoherent, p=2.2e-16, one-sided Mann-Whitney-U). Additionally, the HPD size for the unclassified SWRs was also We note here that while the size of the HPD will be influenced by the dynamic estimated from the data, it remains the case that a continuous or stationary dynamic can correspond to a large HPD region (see outliers in Figure \ref{4}E), indicating less certainty for those specific events.

\begin{figure*}%[tb2]
\centering
\includegraphics[width=0.80\linewidth]{figures/Figure4/Figure4_v6}
\caption{Validation of classification using the 95\% Highest Posterior Density. \textbf{(A-D)}  Examples of the 95 \% Highest Posterior Density. In each column: top panel: Probability of dynamic over time. Shading and labels indicate dynamic categories. Middle panel: Posterior distribution of estimated linear position over time. Magenta dashed line indicates animal's position. Bottom panel: Cumulative HPD size---the integral of the position bins with the top 95\% probable values. \textbf{(E)} Average Cumulative 95\% HPD size for each dynamic category. Median 24 cm for spatially coherent vs. median 238 cm for spatially incoherent, p=2.2e-16, one-sided Mann-Whitney-U}
\label{4}
\end{figure*}

@@

Surprisingly, our results indicate that most events with coherent spatial content are not dominated by the continuous movement dynamic, and thus correspond to trajectories that are stationary or that move relatively slowly compared to their purely continuous counterparts. We therefore examined these events in more detail. We first note that most of the SWRs (16454 of 23382 classified SWRs or 70\%) are well described by a single dynamic or mixtures of dynamics (Figure \ref{5}A). Surprisingly, the most common category is stationary-continuous mixtures (9860 of 23382 classified SWRs or 42\%, Figure \ref{5}A). These events contain representations that move at slower speeds (Figure \ref{5}D; though note these speeds are calculated from the MAP estimate and thus noisy), and are slightly shorter, on average, than events with continuous dynamics (median duration: stationary-continuous-mixture 72 ms vs. continuous 95 ms, Figure \ref{5}B). Nonetheless, both these slow-moving events and continuous events represented locations that were some distance away from the animal (mean trajectory distance from animal's position: stationary-continuous-mixture 51 cm vs. continuous 42 cm, Figure \ref{5}C). This indicates that the trajectories of these SWRs, like ones that have faster continuous dynamics, do not represent the animal's actual position and cannot be explained by erroneously detected SWRs.

@@

Previous work reported that less than half of SWRs or high-population-activity events contained replay \cite{KarlssonAwakereplayremote2009, FosterReversereplaybehavioural2006, DavidsonHippocampalReplayExtended2009}. This could lead one to the assumption that most events are not spatially coherent or meaningful. Our results indicate that this is not the case: in our dataset, the large majority of SWRs (85\%) contained spatially coherent content, as defined by some combination of stationary or continuous dynamics. These events included decoded representations where the most probable positions were highly spatially concentrated. This was in stark contrast to unclassified events or events that included fragmented dynamics, which were associated with highly distributed decoded spatial representations.

@@

\subsection*{Simulated Data}
Encoding data for Figure \ref{1} and Figure \ref{fig:Figure1-Figure supplement 1} were generated by simulating 15 traversals of a 180 cm linear track. The spiking of 19 neurons was simulated using an inhomogeneous Poisson process where the instantaneous firing rate of each neuron changes according to a Gaussian place field. The Gaussian place fields had a variance of 36 cm and were spaced at 10 cm intervals over the 180 cm track. The decoding data for Figure \ref{1}F was generated by simulating 20,000 linear traversals of the 180 cm track, each with a unique constant speed, starting at 0.5 cm/s and increasing by 0.5 cm/s up to 10,000 cm/s. Each simulated neuron "spiked" when the traversal passed through the peak location of its place field.

@@

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=1.0\linewidth]{figures/Figure1-supplemental1/Figure1_v3_supplemental1}
\caption{The model is robust to change of the probability of persisting in the same dynamic for a wide range of plausible expected durations (25 ms to 150 ms). \textbf{(A)} Each plot shows the probability of each dynamic on simulated data example from Figure \ref{1} with a different diagonal value---which governs the probability of remaining in that dynamic. The corresponding expected duration of staying in the dynamic is listed as duration. The off-diagonal values---the probability of switching to one of the other dynamics---are set to be equally likely with the remainder of the probability, as in Figure \ref{1}D. The diagonal increases from left to right, top to bottom, until the case where the diagonal is one and the off-diagonal is zero---i.e. the case where there is no probability of switching to another dynamic. Shaded regions correspond to the classification as in Figure \ref{1}. \textbf{(B)} The probability of position over time for each diagonal value. Conventions the same as in (A).}
\label{fig:Figure1-Figure supplement 1}
\end{figure*}

\begin{figure*}%[tbhp]
\centering
\includegraphics[width=0.80\linewidth]{figures/Figure2-supplemental1/Figure2_v3-supplemental1}
\caption{Decoding the same SWR in Figure \ref{2} with 2D position using sorted spikes and clusterless decoding, respectively. \textbf{(A)} The left plot shows the spikes from cells arranged by the linear position of the peak of place field as in Figure \ref{2}. The middle plot shows the probability of each dynamic over time from the 2D decode. Shaded regions indicate classification category as in Figure \ref{1}G and \ref{2}. The rightmost plot shows the most probable estimate of the latent position (MAP estimate) with color indicating time. The latent position posterior summed over time is shown in the purple shading. The light grey lines represent the position of the animal over the entire epoch and the magenta dot represents the animal's position. \textbf{(B)} Same as in (A), but with clusterless decoding.}
\label{fig:Figure2-Figure supplement 1}
\end{figure*}
